---
output:
  html_document: 
    toc: true
    toc_float: true
---

<link rel="stylesheet" href="styles.css" type="text/css">

Members of our team a wealth of expertise owing to their diverse backgrounds in veterinary science, ecology, spatial epidemiology and mathematical modellings. We apply spatial epidemiology and risk mapping approaches for projects at interface between animal and human public health to develop a broader understanding of what mechanisms influence the geographical distributions of animal and human infections.

## Ricardo Soares Magalhães 
Position: Lab Head

A/Prof Soares Magalhães recent publications
```{r, echo = FALSE, warning=FALSE, message=FALSE}
library(kableExtra)
library(knitr)
source('functions/scholar_allpubs.R')
all_pubs <- scholar_allpubs(c('aAh0t1AAAAAJ&hl'))
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}
kable(data.frame(all_pubs %>%
          dplyr::filter(Year > 2016)), row.names = F,
      format = 'html') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(2, width = '30em') %>%
  column_spec(3, italic = T, width = '20em') %>%
  column_spec(4, width = '20em') %>%
  scroll_box(width = "100%", height = "400px")
```
<br>

## Postdoctoral Fellows
### Nicholas Clark
Dr Clark is a Postdoctoral Fellow interested in spatial epidemiology, molecular ecology and the spread of disease at the human-wildlife interface. His role with the group is to conduct spatial modelling of zoonotic pathogens, primarily Q fever and rabies, as well as to lead efforts to forecast risks of tick infestation for Australian domestic animals. Read more about Dr Clark's work on his [personal website](https://nicholasjclark.weebly.com/) and [Google Scholar](https://scholar.google.com.au/citations?user=5bO9uxEAAAAJ&hl=en) pages.
  
Dr Clark's recent publications
```{r, echo = FALSE, warning=FALSE, message=FALSE}
library(kableExtra)
library(knitr)
source('functions/scholar_allpubs.R')
all_pubs <- scholar_allpubs(c('5bO9uxEAAAAJ'))
```

```{r, echo = FALSE, warning=FALSE, message=FALSE}
kable(data.frame(all_pubs %>%
          dplyr::filter(Year > 2016)), row.names = F,
      format = 'html') %>%
  kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  column_spec(2, width = '30em') %>%
  column_spec(3, italic = T, width = '20em') %>%
  column_spec(4, width = '20em') %>%
  scroll_box(width = "100%", height = "400px")
```
<br>

### Javier Cortes Ramirez
Position:  Postdoctoral Fellow

<br>

## PhD Students
### Pandji Dhewantara 
Position: PhD Student

<br>

### Tarni Cooper
Position: PhD Student

<br>

### Hester Rynhoud
Position: PhD Student

<br>

### Tuhin Biswas
Position: PhD Student

<br>

### Md. Mehedi Hasan
Position: PhD Student

<br>

### Xiaoyan Zhou
Position: PhD Student

<br>

### Kei Owada
Position: PhD Student

<br>

### Alamzewod Assefa Gelaw
Position: PhD Student

<br>

### Andrea Araujonavas
Position: PhD Student

<br>

### Angela M. Cadavid
Position: PhD Student

<br>

## Undergraduate Researchers
### Alex Pekin 
Position: Undergraduate Researcher

<br>

### Carlos Donoghue
Position: Undergraduate Researcher

<br>

### Grace Henry
Position: Undergraduate Researcher

<br>

## Alumni
### Mohamad Assoum 
Position: Alumnus



